---
title: "DECONV DREAM Challenege 2020 (5)"
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_float: true
---



```{r fig.height=8, fig.width=8}
library(gridExtra)
library(ggplot2)
a3$type<-"glmnet200"
a4$type<-"glmnet250"
a5$type<-"glmnet350"
a6$type<-"glmnet500"
a7$type<-"glmnet1000"
a8$type<-"glmnet2500"
a9$type<-"glmnet5000"
a10$type<-"glmnet10000"
a11$type<-"glmnet20000"

x1$type<-"svr200"
x2$type<-"svr250"
x3$type<-"svr300"
x4$type<-"svr500"
x5$type<-"svr750"
x6$type<-"svr1000"
x7$type<-"svr1250"
x8$type<-"svr2000"
x9$type<-"svr5000"



z4$type<-"pls500"
z3$type<-"pls350"
z2$type<-"pls250"
z1$type<-"pls200"

heatmap <-rbind(a3,a4,a5,a6,a7,a8,a9,a10,a11,
                
                x1,x2,x3,x4,x5,x6,x7,x8,x9,
                z1,z2,z3,z4)

 
```


## Heatmap per cell (Pearson)
```{r fig.width=7, message=FALSE, warning=FALSE}
#library(ggplotify)
#par(mfrow=c(2,1))
pattern="DS"

heatmap %>% group_by(type,cells) %>%  summarise(pearson=mean(pearson)) %>% reshape2::acast(type ~cells) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Blues")
```
## Heatmap per cell rnaseq (Pearson)
```{r fig.width=7, message=FALSE, warning=FALSE}

heatmap %>% filter(datasets %in% c("DS446395","DS500","FIAS4")) %>% group_by(type,cells) %>%  summarise(pearson=mean(pearson)) %>% reshape2::acast(type ~cells) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Blues")
```

## Heatmap per cell (Spearman)
```{r fig.width=7, message=FALSE, warning=FALSE}
heatmap %>% group_by(type,cells) %>% summarise(spearman=mean(spearman)) %>% reshape2::acast(type ~cells) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Reds")
```

## Heatmap per cell rnaseq (Spearman)
```{r fig.width=7, message=FALSE, warning=FALSE}
heatmap  %>% filter(datasets %in% c("DS446395","DS500","FIAS4")) %>% group_by(type,cells) %>% summarise(spearman=mean(spearman)) %>% reshape2::acast(type ~cells) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Reds")
```




## Heatmap per dataset (Pearson)
```{r fig.width=7, message=FALSE, warning=FALSE}
#library(ggplotify)
#par(mfrow=c(2,1))
pattern="DS"

heatmap %>% group_by(type,datasets) %>%  summarise(pearson=mean(pearson)) %>% reshape2::acast(type ~datasets) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Blues")
```
## Heatmap per dataset rnaseq (Pearson)
```{r fig.width=7, message=FALSE, warning=FALSE}

heatmap %>% filter(datasets %in% c("DS446395","DS500","FIAS4")) %>% group_by(type,datasets) %>%  summarise(pearson=mean(pearson)) %>% reshape2::acast(type ~datasets) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Blues")
```

## Heatmap per dataset (Spearman)
```{r fig.width=7, message=FALSE, warning=FALSE}
heatmap %>% group_by(type,datasets) %>% summarise(spearman=mean(spearman)) %>% reshape2::acast(type ~datasets) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Reds")
```

## Heatmap per dataset rnaseq (Spearman)
```{r fig.width=7, message=FALSE, warning=FALSE}
heatmap  %>% filter(datasets %in% c("DS446395","DS500","FIAS4")) %>% group_by(type,datasets) %>% summarise(spearman=mean(spearman)) %>% reshape2::acast(type ~datasets) %>% as.matrix() %>% d3heatmap::d3heatmap(colors = "Reds")
```






## x6 [svr1000] Results for svr radial noscale 1000 features over 20000 (RF2) 
```{r message=FALSE, warning=FALSE}
filename<-"./devcon_challenge.svr_results_rf_selected_features_1000_20000_noscale_newmix_spearson_coarsegrain.csv"
readr::write_csv(RESULTS,path = filename)
x6<- readr::read_csv(filename)  %>%  mutate(pearson=ifelse(is.na(pearson),0,pearson),
                                      spearman=ifelse(is.na(spearman),0,spearman)
                                      ) 
x6
x6 %>% summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
x6 %>% filter( datasets %in% c("DS446395","DS500","FIAS4")) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

## x7 [svr1500] Results for svr radial noscale 1000 features over 20000 (RF2) 
```{r message=FALSE, warning=FALSE}
filename<-"./devcon_challenge.svr_results_rf_selected_features_1500_20000_noscale_newmix_spearson_coarsegrain.csv"
#readr::write_csv(RESULTS,path = filename)
x7<- readr::read_csv(filename)  %>%  mutate(pearson=ifelse(is.na(pearson),0,pearson),
                                      spearman=ifelse(is.na(spearman),0,spearman)
                                      ) 

x7
x7 %>% summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
x7 %>% filter( datasets %in% c("DS446395","DS500","FIAS4")) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

## x8 [svr2000] Results for svr radial noscale 2000 features over 20000 (RF2) 
```{r message=FALSE, warning=FALSE}
filename<-"./devcon_challenge.svr_results_rf_selected_features_2000_20000_noscale_newmix_spearson_coarsegrain.csv"
#readr::write_csv(RESULTS,path = filename)
x8<- readr::read_csv(filename) # %>%  mutate(pearson=ifelse(is.na(pearson),0,pearson),
                               #       spearman=ifelse(is.na(spearman),0,spearman)
                               #      ) 

x8
x8 %>% summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
x8 %>%  filter( datasets %in% c("DS446395","DS500","CIAS4","CIVA3"))  %>% summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```



