---
title: "Devcon Challenge"
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
---

```{r}

```

# Results for liblinear using a full set of  features (noscale) ( 12 - L2-regularized L2-loss support vector regression (dual))
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_12_results_noscale_all_lines.csv")
a0<-readr::read_csv("./devcon_challenge.liblinear_12_results_noscale_all_lines.csv") %>% filter(!is.na(pearson)) 
a0
readr::read_csv("./devcon_challenge.liblinear_12_results_noscale_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```


# Results for liblinear  (noscale) 1500 features.  ( 12 - L2-regularized L2-loss support vector regression (dual))
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_12_results_noscale_rf_selected_features_1500_all_lines.csv")
a6<-readr::read_csv("./devcon_challenge.liblinear_12_results_noscale_rf_selected_features_1500_all_lines.csv") %>% filter(!is.na(pearson)) 
a6
readr::read_csv("./devcon_challenge.liblinear_12_results_noscale_rf_selected_features_1500_all_lines.csv") %>% filter(!is.na(pearson))  %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```


# Results for liblinear  (noscale) 1000 features. (13 L2-regularized L1-loss support vector regression (dual))
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1000_all_lines.csv")
a1<-readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1000_all_lines.csv") %>% filter(!is.na(pearson)) 
a1
readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```



# Results for liblinear  (noscale) 1500 features. (13 L2-regularized L1-loss support vector regression (dual))
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1500_all_lines.csv")

a2<-readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1500_all_lines.csv") %>% filter(!is.na(pearson)) 
a2
readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_1500_all_lines.csv") %>% filter(!is.na(pearson))  %>% summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))

```

# Results for liblinear  (noscale) 2000 features. (13 L2-regularized L1-loss support vector regression (dual))

```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_2000_all_lines.csv")

a3<-readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_2000_all_lines.csv") 
a3
readr::read_csv("./devcon_challenge.liblinear_13_results_noscale_rf_selected_features_2000_all_lines.csv")  %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

# Results for glmnet using 5000 features
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.gmlnet_results_noscale_rf_selected_features_5000_all_lines.csv")
a4<-readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_5000_all_lines.csv") %>% filter(!is.na(pearson)) 
a4
readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_5000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

# Results for glmnet using 500 features
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_all_lines.csv")
a5<-readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_all_lines.csv") 
a5
readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```




# Results for RF  ~1500 features per tree over ~20000 features
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.rf_results_all_lines.csv")
r1<-readr::read_csv("./devcon_challenge.rf_results_all_lines.csv") %>% filter(!is.na(pearson)) 
r1
readr::read_csv("./devcon_challenge.rf_results_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))

```

# Results for glmnet using 500 features over 20000
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_20000_all_lines.csv")
r2<-readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_20000_all_lines.csv") 
r2
readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_500_20000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

# Results for glmnet using 1000 features over 20000
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1000_20000_all_lines.csv")
r3<-readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1000_20000_all_lines.csv") 
r3
readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1000_20000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```
# Results for glmnet using 1500 features over 20000
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1500_20000_all_lines.csv")
r4<-readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1500_20000_all_lines.csv") 
r4
readr::read_csv("./devcon_challenge.gmlnet_results_noscale_rf_selected_features_1500_20000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

# Results for liblinear 13 using 100 features over 20000
```{r message=FALSE, warning=FALSE}
#readr::write_csv(RESULTS,path = "./devcon_challenge.liblinear_results_noscale_rf_selected_features_100_20000_all_lines.csv")
r5<-readr::read_csv("./devcon_challenge.liblinear_results_noscale_rf_selected_features_100_20000_all_lines.csv") 
r5
readr::read_csv("./devcon_challenge.liblinear_results_noscale_rf_selected_features_100_20000_all_lines.csv") %>% filter(!is.na(pearson)) %>%  summarise(pearson_mean=mean(pearson),spearman_mean=mean(spearman))
```

```{r fig.height=8, fig.width=8}
library(gridExtra)
a0$type<-"liblinear12full"
a1$type<-"liblinear13_1000"
a2$type<-"liblinear13_1500"
a3$type<-"liblinear13_2000"
a4$type<-"glmnet5000"
a5$type<-"glmnet500"
a6$type<-"liblinear12_1500"
r1$type<-"rf_1500_20000"
r2$type<-"glmet500_20000"
r3$type<-"glmnet1000_20000"
r4$type<-"glmnet1500_20000" 
r5$type<-"liblinear13_100_20000" 

plot2<-rbind(a0,a1,a2,a3,a4,a5,a6,r1,r2,r3,r4,r5) %>% group_by(type,datasets) %>% summarise(pearson=mean(pearson)) %>% arrange(pearson) %>%
  ggplot()+
  geom_tile(aes(x=type,y=datasets,fill=pearson))+
  scale_fill_gradient(low = "red", high = "white",limits=c(0.4, 1),)+
  theme(axis.text.x=element_text(angle=45,hjust=1))
  
  
plot1<-rbind(a0,a1,a2,a3,a4,a5,a6,r1,r2,r3,r4,r5) %>% group_by(type,datasets) %>% summarise(spearman=mean(spearman)) %>% arrange(spearman) %>%
  ggplot()+
  geom_tile(aes(x=type,y=datasets,fill=spearman))+
  scale_fill_gradient(low = "red", high = "white",limits=c(0.4, 1),)+
  theme(axis.text.x=element_text(angle=45,hjust=1))

gridExtra::grid.arrange(plot1,plot2,ncol=2)  
  
```
